Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-11-03 manuscript/text_reuse.tex
updated paper and one new figure

\subsection{Tasks}
\begin{itemize}
\item
\end{itemize}

@@

How ever, it is not clear, how well text reuse is suited to to detect real
policy diffusion. There are several complications that we are addressing in this
paper. First, every bill has procedural content that is not related to the
policy content of the bill. Since every state legislature has a set of such
standard or boiler plate text in each bill, there will be significant text reuse
between bills in the same state and possibly also between bills from different
states. Second, it is not obvious how much text reuse will mean substantive
policy overlap. Given that each bill pair has a continuous proportion of
overlapping text, setting the threshold too low might mean to classify bills as
equivalent that are only in the same policy area, or are on a similar issue, but
are opposed in content. On the other hand, setting the threshold too high could
mean overlooking equivalent bills because of small insignificant changes to the
text.

@@

\subsection{Tasks}
\begin{itemize}
\item Policy diffusion (FL expand paragraph)
\item Text re-use in CBP in bills 
\item Text re-use in general
\begin{itemize}
\item Plaigirism
\item Alignment (FL expand review of Wilkerson et al)
\end{itemize} 
\item Discussion of text-based classification
\end{itemize}

@@

In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al. (2015) and the Sunlight foundation. This data base contains approximately 500,000
bills from 2008 to 2015. The available metadata for the bills includes a timestamp for introduction and approval of the bill, the name and party affiliation of the sponsor(s), the state and the bill id.

This collection of bills is based on all bills that are available through the \url{openstates.org} API. Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted. The database contains the full bill text and the following additional metadata:

\begin{itemize}
    \item action\_dates:
        \begin{itemize}
            \item first
            \item last
            \item passed lower
            \item passed upper
            \item signed
        \end{itemize}
    \item actions (a list of legislative actions. E.g. referred to a committee)
        \begin{itemize}
            \item actor
            \item date 
            \item related\_entities 
            \item type
        \end{itemize}
    \item bill document first
    \item bill document last
    \item bill id
    \item bill title
    \item date created
    \item date introduced
    \item date signed
    \item date updated
    \item session
    \item short title
    \item state
    \item summary
    \item sunlight\_id
    \item unique id
\end{itemize}

For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}. The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.

>>>>

@@

How ever, it is not clear, how well text reuse is suited to to detect real
policy diffusion. There are several complications that we are addressing in this
paper. First, every bill has procedural content that is not related to the
policy content of the bill. Since every state legislature has a set of such
standard or boiler plate text in each bill, there will be significant text reuse
between bills in the same state and possibly also between bills from different
states. Second, it is not obvious how much text reuse will mean substantive

policy overlap. Given that each bill pair has a continuous proportion of
overlapping text, setting the threshold too low might mean to classify bills as
equivalent that are only in the same policy area, or are on a similar issue, but
are opposed in content. On the other hand, setting the threshold too high could
mean overlooking equivalent bills because of small insignificant changes to the
text.

@@

\subsection{Tasks}
\begin{itemize}
\item Policy diffusion (FL expand paragraph)
\item Text re-use in CBP in bills 
\item Text re-use in general
\begin{itemize}
\item Plaigirism
\item Alignment (FL expand review of Wilkerson et al)

\citet{wilkerson2015tracing} use the

\end{itemize} 
\item Discussion of text-based classification
\end{itemize}

@@

\textit{Bill text}\\
In order to calculate the alignment scores between bills, we rely on a database collected by Burgess et al. (2015) and the Sunlight foundation. This data base contains approximately 500,000 bills from 2008 to 2015. The available metadata for the bills includes a timestamp for introduction and approval of the bill, the name and party affiliation of the sponsor(s), the state and the bill id.  This collection of bills is based on all bills that are available through the \url{openstates.org} API. Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted. The database contains the bill text as well as additional information on the legislative process for the bill. We have the first and the last version of the bill text, the sponsor of the bill and all legislative action that was taken on the bill.

\textit{Alignments}\\
The alignment scores are calculated using the affine version of the local alignment algorithm proposed by \citet{smith1981identification} in order to match genetic sequences. The same algorithm has been used by \citet{wilkerson2015tracing} to trace bills through the legislative process in congress. When considering two bills, the algorithm treats each bill as a sequence of words and tries to find the best alignment between these two sequences. \citet{wilkerson2015tracing} split the bills into sections and search for text reuse across sections. Since this results in about 7 billion possible pairs, first filter out pairs that don't have an exact match of a sequence of at least ten words. We encounter the same problem in our analysis to a greater extent. Assuming each bill consists of ten sections on average, there would be approximately $1.25 * 10^{12}$ possible pairs of sections.

In order to assess the computational burden the local alignment algorithm poses we test the implementation of the alignment algorithm (Burgess et al. 2015) on a set of 1000 randomly selected bills. In a first pass we calculate the alignments  between all pairs of the full bills (not divided into sections). Figure \ref{fig:time_size} displays the relationship between bill length and computation time. As expected the time increases exponentially with the length of the bills. Figure \ref{fig:time} displays a histogram of the logarithm of the computation time (in seconds). Computation time varies between $0.001s$ and $1,650s$ with $75\%$ of the distribution below $0.1s$ and a median time of $0.03s$.  This shows that an exhaustive comparison of just the full bills (not separated into sections) would take about 100 years on a single machine.

\begin{figure}[ht!]
    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time_size_selection.png}}
\caption{Computation time for selection of bills. The Colors correspond to five selected bills (focus bill or left bill). For each of the bills, the best alignment with 1000 randomly selected bills (right bills) are calculated. The size of the dots corresponds to the logarithm of the length of the focus bill (in number of words), the x-axis corresponds to the logarithm of the size of the comparison bill and the y-axis corresponds to the logarithm of the computation time (in seconds).}
\label{fig:time_size}
\end{figure}

\begin{figure}[ht!]
    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/time.png}}
\caption{Histogram of computation time for all analyzed bills.}
\label{fig:time} 
\end{figure}

Since for this calculation there is no minimum threshold (as in \citet{wilkerson2015tracing} minimum of 10 words). Alignments between almost all bills are found and most of the alignments are procedural language. This is apparent in Figure \ref{fig:state_to_state} which displays the average alignment score for bills from Illinois (left panel) and Washington (right panel) for all other states in the sampled data set (x-axis). Especially for Illinois there is a much higher alignment score for bills from the same state. This shows that a minimum threshold and a classifier for procedural language are necessary.

\begin{figure}[ht!]
    \makebox[\textwidth]{\includegraphics[width=\textwidth]{figures/state_to_state.png}}
\caption{Average alignment scores between states. The left panel corresponds to `left bills' from Illinois, the right panel to bills from Washington. Each bar displays the average score of the best alignment found between bills of the states.}
\label{fig:state_to_state} 
\end{figure}

In order to make the computation more feasible, we rely on a similar strategy as \citet{wilkerson2015tracing}. Our bills are stored in an elastic search database wich provides a variety of search algorithms that are designed to find similar documents. Since the seraching the whole database for the full document is very time consuming the following search algorithm is used to first find a pre selection of similar bills that are then exhaustively checked for text reuse:

\begin{enumerate}
\item All bills are stored in the database in n-grams of size 2-5
\item Select the 25 n-grams with the highest tf-idf score in the query document
\item Calculate a score slightly adapted cosine similarity score between the selected n-gram vector and all full document n-gram vectors in the database\footnote{See \url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html} for details on the similarity scoring in Elastic Search}
\end{enumerate}

\subsection*{Tasks}

\begin{itemize}
    \item Augment the timing dataset with the document similarity scores
    \item

\textit{Ideological Scores}\\
For the ideological matching, we rely on latent ideology scores measured by \citep{shor2011}. The data set contains scores for 20738 legislators from 50 state legislatures as well as their party affiliation and their time in office.
